timesliced_random_cell_selection

### 2018-12-06 src/timesliced_random_cell_selection.Rmd
line 210 - to redo background

```{r timesliced unique unsampled}
no_timeslices <- length(split_cell_yymm) # how many levels (time slices) are in the list
bckoutput <- "../output/bio/background/raw/" #where the files are to be saved to
for (i in 1:no_timeslices){
  timeslice <- split_cell_yymm[[i]]
  timeslice <- as.data.frame(timeslice)
  time_cell <- unique_cell_xyz
  time_cell <- time_cell[!time_cell$id_depth %in% timeslice$id_depth, , drop = FALSE]
  write.csv(time_cell, paste0(bckoutput, names(lapply(split_cell_yymm, names))[i], ".csv"), row.names = FALSE) 
}
```

>>>>

## XXX SAM THIS IS THE CODE THAT NEEDS EDITING - I THINK JUST REMOVE THE LINE #

```{r timesliced unique unsampled}
no_timeslices <- length(split_cell_yymm) # how many levels (time slices) are in the list
bckoutput <- "../output/bio/background/raw/" #where the files are to be saved to
for (i in 1:no_timeslices){
  timeslice <- split_cell_yymm[[i]]
  timeslice <- as.data.frame(timeslice)
  time_cell <- unique_cell_xyz
  #time_cell <- time_cell[!time_cell$id_depth %in% timeslice$id_depth, , drop = FALSE]
  write.csv(time_cell, paste0(bckoutput, names(lapply(split_cell_yymm, names))[i], ".csv"), row.names = FALSE) 
}
```
